A weakly structured stem for human origins in Africa

### 2023-01-14 paper.tex
model clarifications

We began with a model of geographic expansion from a single ancestral,
unstructured source followed by migration between populations, without allowing
for contribution from an African archaic hominin lineage or population
structure prior to the expansion (Figure~\ref{fig:proposed-models}A or
Figure~\ref{fig:proposed-models}D). As expected \citep{Ragsdale2019-nt}, this
first model was a poor fit to the data qualitatively
(Figure~\ref{fig:supp-single-origin-fits}) and quantitatively (log-likelihood
($LL$) $\approx -189,300$, Table~\ref{tab:supp-single-origin}).  We next
explored a suite of parameterized models in which population structure predates
the differentiation of contemporary groups (Supporting Information (SI)
Section~\ref{sec:modelspec}).  Depending on the parameters, these encompassed
models allowing for ancestral reticulation (such as
fragmentation-and-coalescence or meta-population models,
Figure~\ref{fig:proposed-models}B), archaic hominin admixture
(Figure~\ref{fig:proposed-models}C), and African multi-regionalism
(Figure~\ref{fig:proposed-models}D).

>>>>

We began with a model of geographic expansion from a single ancestral,
unstructured source followed by migration between populations, without allowing
for contribution from an African archaic hominin lineage or population
structure prior to the expansion (Figure~\ref{fig:proposed-models}A or
Figure~\ref{fig:proposed-models}D). As expected \citep{Ragsdale2019-nt}, this
first model was a poor fit to the data qualitatively
(Figure~\ref{fig:supp-single-origin-fits}) and quantitatively (log-likelihood
($LL$) $\approx -189,300$, Table~\ref{tab:supp-single-origin}). We next
explored a suite of parameterized models in which population structure predates
the differentiation of contemporary groups (Supporting Information (SI)
Section~\ref{sec:modelspec}).  Depending on the parameters, these encompassed
models allowing for ancestral reticulation, such as
fragmentation-and-coalescence or meta-population models
(Figure~\ref{fig:proposed-models}B), archaic hominin admixture
(Figure~\ref{fig:proposed-models}C), and African multi-regionalism
(Figure~\ref{fig:proposed-models}D). The recent expansion and the African
multi-regional models (Figure~\ref{fig:proposed-models}A and D) have the same
topology, so interpretation of the model depends on the specified or inferred
divergence times.
